---
title: "Prototype for the Big Mac exchange-rate index"
author: "D. Kaplan"
date: "1/16/2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

##  Introduction

> *"Premature optimization is the root of all evil."* -- Donald Knuth

I like to  prototype shiny apps as an Rmd document. This has several advantages:

* Avoids start-up work of arranging a UI.
* Makes it easy to include narrative, including comments on the design from your co-workers.
* Let's you display the code as you like.

For some clients, a document is the way to go, anyways.


```{r load_data, message = FALSE}
# NOTE: If you want to deploy this app on a server (e.g. shinyapps.io)
#       you need to move all data files needed into the app's directory
month_names <- c("Jan", "Feb", "Mar", "Apr", "May", "June", "July", "Aug", "Sept", "Oct", "Nov", "Dec")

Raw <- readr::read_csv("../../../data/big-mac-index.csv")
Big_mac_data  <- 
  Raw %>%
  mutate(year  = lubridate::year(date),
         month = month_names[lubridate::month(date)])
```



This chunk is going to create some controls. Note that since the controls are ultimately HTML, I can create them in one place and display them in another.

```{r make_controls, eval = TRUE}
countries <- unique(Big_mac_data$name)
years <- unique(Big_mac_data$year)
months <-  unique(Big_mac_data$month)
country <- selectInput("countries", "Comparison countries:", choices = countries, multiple = TRUE )
year  <- selectInput("year", "Year:", choices = years)
month <- selectInput("month", "Months:", choices = months, multiple = TRUE)
```

`r country` | `r year` | `r month`
------------|----------|----------
Choose many | Just 1   | As many as you like.

Comment: Watch out. You'll have to reset the choices for "Months" whenever a new year is selected.

```{r some_server_code}
for_one_year <- reactive(Big_mac_data %>% filter(year %in% input$year))
observe({
  updateSelectInput(session, inputId = "month", choices = unique(for_one_year()$month))
})
```

