---
title: "Not Yet a Dashboard"
output: 
  html_document: 
    theme: journal
---

```{r setup, include=FALSE}
# library(flexdashboard)
library(tidyverse)
library(xts)
```


### What's this about?

Add in a video playing <https://www.youtube.com/embed/U3ZaNcSkttw>

Hints:

* No R code needed!
* In your browser, navigate to the video
* Under "Share" select "embed"
* Copy the HTML iframe code

### For dashboard

IGNORE this section until we come to the "As a Dashboard" activity

1. Uncomment `library(flexdashboard)` above.
2. Move this to the YAML section, replacing `html_document`

```
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
```

### Map

Put a map of Austin, TX here.

Hint:

* Use `leaflet` package to generate the widget
* Latitude/Longitude of Austin: 30.27° N, 97.75° W
* Functions to use: `leaflet::leaflet()`, `setView()`, `addTiles()`
  * alternative to `setView()`: use `addMarkers()` and let the server figure out the initial scale.

```{r drawAustin}
library(leaflet)
# Your commands go here
```

### Big Mac Index

Hints:

* Use `plotly` library.
* Create a ggplot2 graphic like the one below.
* call `ggplotly()` with the graphic as an argument

```{r echo = FALSE}
Big_mac <- read_csv("../data/big-mac-index.csv")
countries <- c("Sweden", "Norway", "Russia", "United States", "Korea", "Japan", "Malaysia", "India", "China", "Pakistan", "Taiwan", "Britain", "Ecuador", "Argentina")
Just_my_countries <-
  Big_mac %>%
  filter(name %in% countries) %>%
  mutate(year = lubridate::year(date), month = lubridate::month(date)) %>%
  filter(year == 2017) %>%
  select(name, month, dollar_price) %>%
  tidyr::spread(key = month, value = dollar_price) %>%
  mutate(name = reorder(name, `7`, I) )
My_graphic <- 
  ggplot(data = Just_my_countries, aes(y = name)) +
  geom_segment(aes(x = `1`, xend = `7`, y = name, yend = name)) +
  geom_point(aes(x = `1`), color = "red", size = 5) +
  geom_point(aes(x = `7`), color = "blue", size = 5) +
  labs(x = "Price in USD")
# Add a line here to display My_graphic
```

### Time Series

```{r time_series}
# A demo
library(dygraphs)
Apple <- read_csv("../data/AAPL.csv") 
Apple <- Apple %>%  as.xts(order.by = Apple$Date) 
dygraph(Apple[ , c("Low", "High", "Close")], "Apple stock price") %>%
  dySeries() %>%
  dyRangeSelector(height = 20)
```
