---
title: "San Diego Burritos - Parametrized"
author: "Mine Çetinkaya-Rundel"
date: "`r Sys.Date()`"
output: 
  html_document: 
    highlight: pygments
    theme: cosmo
params:
   Reviewer: 
     label: "Reviewer:"
     value: Scott
     input: select
     choices: [Scott, Emily, Ricardo, Sage, Luis, Richard]
---

```{r load-packages, message=FALSE}
library(tidyverse)
```

## Kaggle: SD Burritos

The data come from [Kaggle.com](https://www.kaggle.com/srcole/burritos-in-san-diego). In this analysis we focus on burritos reviewed by `r params$Reviewer` only.

```{r load-filter-data, message=FALSE, warning=FALSE}
burritos <- read_csv("../data/burritos_01022018.csv") %>%
  filter(Reviewer == params$Reviewer)
```

The data set contains `r nrow(burritos)` burritos reviewed by `r params$Reviewer` 
from `r burritos %>% count(Location) %>% nrow()` restaurants.

The scatterplot below displays the relationship between the cost and overall 
rating of the burritos for burritos reviewed by `r params$Reviewer`.

```{r rating-cost-scatter, warning=FALSE}
ggplot(data = burritos, mapping = aes(x = Cost, y = overall)) +
  geom_point() +
  labs(title = "Overall rating vs. cost", y = "Overall rating")
```
