---
title: "R in Markdown"
author: "Danny Kaplan"
date: "January 15, 2019"
output:
  html_document:
    highlight: pygments
    theme: cosmo
---

```{r load-packages}
library(tidyverse)
library(shiny)
```

## Preliminary tasks

1. It's a good practice to load the major packages for a document in a "setup" or "load packages" chunk. But the output from that chunk is a poor way for a reader to start off with a document.
    * Add a chunk option to `load-packages` to suppress the output. (Hint: the option begins with `i`.)
2. Add an inline R chunk to your document so that the current date/time show up here: XXXX. Try to put the date in italics.

## Add a plot chunk

3. Make chunk producing a simple plot using the `mtcars` data frame built into R.

## Inline code

Typical uses of inline code ...

1. Avoiding hard-coding of numbers. (They become out of date.)
    - Bad: Our analysis involved 51 cars.
    - Better: Our analysis involved `r nrow(mtcars)` cars.
    
    
```{r car_t_test, echo = FALSE}
mod <- lm(mpg ~ disp + cyl, data = mtcars)
```

2. Reporting of results calculated elsewhere.
    - Bad: Keeping displacement constant, an additional cylinder is associated with a loss of about 1.6 miles-per-gallon.
    - Better: ...with a `r ifelse(coef(mod)["cyl"] > 0, "gain", "loss")` of about `r round(abs(coef(mod)["cyl"]), 1)` miles-per-gallon.

**Stretch goal**: Update the date field in the YAML so that the date at the time of knitting the document is printed. (Hint: You can put YAML strings in quotation marks.)


## Add a table chunk

5. Display the first 5 rows of the `mtcars` data frame.


```{r the_table}
knitr::kable(head(mtcars))
```


**Stretch goal**: Modify the chunk with the table to prettify the display. There are many possibilities but try `knitr::kable()`.



## When your code goes wrong

A chunk with an error ...

```{r neg_logs, eval = FALSE}
log(-10)
```

... and another such chunk.

```{r another_error, eval = FALSE}
sqrt(-5)
```
